%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Unit Manager(Cyber Security Solution Ankara)} % Job title
    {Cyberwise Inc.} % Organization
    {Ankara, Turkiye} % Location
    {Mar. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provide to become great team player for my team colleagues each together and also guiding to their career, technical skills and learning more than current times.}
        \item {Generally, i take responsibility for some critical situations for our customers and take action and help my colleagues.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Cyber Security Consultant} % Job title
    {Cyberwise Inc.} % Organization
    {Ankara, Turkiye} % Location
    {Mar. 2020 - Mar. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Fortinet Fortigate - FortiMail - FortiWeb etc. Install, Configure and Manage}
        \item {PaloAlto Firewall - Panorama Install, Configure and Manage}
        \item {PaloAlto Prisma Cloud(Container Security) Install, Configure and Manage}
        \item {Veritas Datainsight Install, Configure and Manage}
        \item {IBM Guardium FAM \& DBF Install, Configure and Manage}
        \item {Broadcom Symantec Endpoint Protection Install, Configure and Manage}
        \item {Broadcom Symantec Endpoint Detection and Response Install, Configure and Manage}
        \item {Broadcom Symantec Thread Defense for Active Directory Install, Configure and Manage}   
        \item {Broadcom Symantec Data Loss Prevention Install, Configure and Manage}
        \item {Broadcom Symantec Messaging Gateway Install, Configure and Manage}
        \item {Broadcom Symantec Mail Security for Microsoft Exchange Install, Configure and Manage}
        \item {Broadcom Symantec Proxy SG Advanced Secure Gateway Install, Configure and Manage}
        \item {Broadcom Symantec Content Analysis Install, Configure and Manage}
        \item {Broadcom Symantec Malware Analysis Sandbox Install, Configure and Manage}
        \item {National Firewall Testing for Acrediate and Product Certification}
        \item {Nessus Pro \& Tenable SC Install, Configure and Manage}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Senior Information Technology Specialist} % Job title
    {Innova Inc.} % Organization
    {Ankara, Turkiye} % Location
    {Dec. 2016 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Active Directory Domain and Services Configure and Manage}
        \item {Microsoft Exchange Server 2016/2019 Install, Configure and Manage}
        \item {Microsoft Skype for Business 2016/2019 Configure and Manage}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Senior Sytem Administrator} % Job title
    {Ministry of Interrior} % Organization
    {Ankara, Turkiye} % Location
    {Jun. 2017 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Active Directory Domain and Services (External \& Intenal DNS's Install, Configure and Manage)}
        \item {Microsoft Exchange Server 2016/2019 Install, Configure and Manage}
        \item {Symantec Broadcom Messaging Gateway Install, Configure and Manage}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {System Administrator} % Job title
    {Mobiliz Inc.} % Organization
    {Ankara, Turkiye} % Location
    {Jan. 2013 - Oct. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Debian / Ubuntu /Centos OSs Install, Configure and Manage}
        \item {Webmin / Bind DNS Services Install, Configure and Manage}
        \item {Apache and Nginx Reverse Proxy Services for WebServers Install, Configure and Manage}
        \item {OpenVPN Install for Corporate Users Install, Configure and Manage}
        \item {pfSense firewall install, maintained and managed Install, Configure and Manage}
        \item {DELL Sonicwall Suppermassive 9000 Series Firewall Configure and Manage}
        \item {VMware ESXi and HyperV Install, Configure and Manage}
        \item {NetAPP and Huawei OceanStore managing for Virtualization Platforms}
        \item {Windows Server 2008/2012/2016 Install, Configure and Manage}
        \item {Office 365 Migrations}
        \item {I haved configure to IPSEC Connection, between the Mobile APNs to Local Server Networks for vehicle tracking}
      \end{cvitems} 
    }
%---------------------------------------------------------

\cventry
    {System Support Engineer} % Job title
    {Nira Information Technology} % Organization
    {Ankara, Turkiye} % Location
    {Oct. 2009 - Dec. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Active Directory Domain and Services Install, Configure and Manage)}
        \item {Fortigate Install, Configure and Manage}
        \item {NAS Devices Install, Configure and Manage}
        \item {Active Directory Implementation Prject at Ministry of Transport}
        \end{cvitems} 
    }
%---------------------------------------------------------
 \cventry
    {Project Technician} % Job title
    {Ekin Inc.} % Organization
    {Ankara, Turkiye} % Location
    {Oct. 2009 - Dec. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {CCTV, IPCam, Switch and Monitoring Servers Install, Configure and Manage)}
        \item {Ankara City Security Management System (KGYS-MOBESE) Projects Implementation}
      \end{cvitems} 
    }
%---------------------------------------------------------
\end{cventries}