%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Unit Manager(Cyber Security Solution Ankara) } % Job title
    {Cyberwise Inc.} % Organization
    {Ankara, Turkiye} % Location
    {Mar. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provide to become great team player for my team colleagues each together and also guiding to their career, technical skills and learning more than current times.}
        \item {At the same time, I take responsibility for some critical situations for our customers and take action and help my business people.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Cyber Security Consultant} % Job title
    {Cyberwise Inc.} % Organization
    {Ankara, Turkiye} % Location
    {Mar. 2020 - Mar. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I was provide the installation, support and maintenance activities of the products under my responsibility among the products supported by the Cyber Security Solutions Ankara Teams}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Senior Information Technology Specialist} % Job title
    {INNOVA} % Organization
    {Ankara, Turkiye} % Location
    {Dec. 2016 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I worked as System Administrator in the Microsoft Services Solutions Department.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Senior Sytem Administrator} % Job title
    {Ministry of Interrior} % Organization
    {Ankara, Turkiye} % Location
    {Jun. 2017 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I worked as System Administrator in the System Management Department under the General Directorate of Information Technologies.}
        \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {System Administrator} % Job title
    {Mobiliz Inc.} % Organization
    {Ankara, Turkiye} % Location
    {Jan. 2013 - Oct. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {My main responsibilities were to ensure the continuity of the system infrastructure}
      \end{cvitems}
%---------------------------------------------------------
\end{cventries}